% !TeX root = ../main.tex

\section{Conclusions}

Currently, a major physical and computational challenge in astrophysics is that high-resolution solar observations, such as those obtained by the \textit{Sunrise} balloon-borne telescope, inevitably suffer from optical degradation due to light diffraction and residual instrumental aberrations. Counteracting these effects through computational deconvolution is imperative to accurately infer the solar magnetic field configuration from the captured spectropolarimetric data. While traditional deconvolution techniques---including Fourier, Wiener, and Richardson-Lucy filters---were systematically implemented and evaluated within this work, they proved insufficient for recovering the complete underlying magnetic topology. Specifically, these classical methods fail to accurately restore the Stokes $V$ profiles due to their intrinsic antisymmetric bipolar nature and the mathematical limitation that the spatial convolution operator cannot isolate the physical parameters algebraically.

To overcome these inherent limitations, the core of this project focused on developing a distinct forward modeling methodology that directly couples the physics of polarized radiative transfer with the optical properties of the instrument. Building upon and adapting van Noort's spatially coupled inversion framework, this approach successfully bypasses the direct spatial deconvolution of the observed Stokes parameters. By formulating the corresponding Jacobian matrix strictly as a linear operator acting on the parameter space rather than constructing and storing it explicitly, the highly parameterized optimization problem was efficiently resolved. This algorithmic formulation enabled the implementation of iterative Krylov subspace methods, specifically the Conjugate Gradient algorithm, to converge toward a robust physical solution guided by the analytical gradient.

The computational performance of this coupled forward method yielded highly satisfactory results when rigorously evaluated within a controlled synthetic environment. By purposefully degrading simulated solar atmospheres to mimic real observational constraints and subsequently applying the developed pipeline, a clear structural recovery and re-concentration of the scattered magnetic flux were demonstrated. Nevertheless, these improvements must be interpreted with academic prudence. Since this inverse problem remains inherently ill-conditioned, the forward mapping approach is subject to limitations, such as a susceptibility to overfitting or the potential amplification of high-frequency noise. Consequently, establishing precise stopping criteria for the iterative solver is crucial to prevent the introduction of unphysical numerical artifacts.

Looking forward, this methodology offers substantial avenues for technical advancement and broader astrophysical applications. While foundational algorithms like Richardson-Lucy were utilized as a baseline reference in this study's pipeline, future iterations could integrate more sophisticated regularization techniques and inversion algorithms currently in active development. Optimizing the computational efficiency and understanding the precise operational bounds of this coupled method will facilitate faster, more scalable studies of the weak solar magnetic field. Furthermore, because this approach relies on a self-consistent physical model rather than purely empirical image processing, its underlying framework holds significant potential beyond solar spectropolarimetry. Provided that the physical system under study exhibits linearity with respect to the local state variables being optimized, this forward modeling architecture can be generalized to other scientific domains, representing a highly successful and robust framework for extracting complex physical parameters directly from fundamental governing equations.